Plots for \enquote{Arrows for Parallel Computations}

### 2017-11-29 paper/separate_plots/main.tex
wip separate plots

\meanOverheadPlot{Mean Overhead for distributed \rmtest 44497 256}{0.02}{32}{272}{../content/benchmarks/distributed-rm/44497-256-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for distributed \jacobitest 4253}{0.5}{32}{272}{../content/benchmarks/distributed-jacobi/3-4253-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for distributed \jacobitest 3217}{0.5}{32}{272}{../content/benchmarks/distributed-jacobi/3-4253-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for distributed \torustest 4096}{0.5}{32}{272}{../content/benchmarks/distributed-torus/4096-diff.csv}

>>>>

\subsection{Distributed}

\subsubsection{\rmtest}

\meanOverheadPlot{Mean Overhead for distributed \\ \rmtest 44497 256}{0.02}{32}{272}{../content/benchmarks/distributed-rm/44497-256-diff.csv}

\subsubsection{\jacobitest}

\meanOverheadPlot{Mean Overhead for distributed \\ \jacobitest 4253}{0.5}{32}{272}{../content/benchmarks/distributed-jacobi/3-4253-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for distributed \\ \jacobitest 3217}{0.5}{32}{272}{../content/benchmarks/distributed-jacobi/3-4253-diff.csv}

\subsubsection{\torustest}

\meanOverheadPlot{Mean Overhead for distributed \\ \torustest 4096}{0.5}{32}{272}{../content/benchmarks/distributed-torus/4096-diff.csv}

\subsection{Shared-Memory}

\subsubsection{\rmtest}

\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 32 vs Eden CP}{0.5}{4}{18}{../content/benchmarks/sm-rm/eden-cp-11213-32-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 64 vs Eden CP}{0.5}{4}{18}{../content/benchmarks/sm-rm/eden-cp-11213-64-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 32 vs GpH}{0.5}{4}{18}{../content/benchmarks/sm-rm/mult-11213-32-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 64 vs GpH}{0.5}{4}{18}{../content/benchmarks/sm-rm/mult-11213-32-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 32 vs Par Monad}{0.5}{4}{18}{../content/benchmarks/sm-rm/par-11213-32-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 64 vs Par Monad}{0.5}{4}{18}{../content/benchmarks/sm-rm/par-11213-32-diff.csv}

    %benchmarks/sudoku-sm
    %    "eden-cp-1000-diff.csv"
    %"eden-cp-16000-diff.csv"
    %"mult-1000-diff.csv"
    %"mult-16000-diff.csv"
    %"par-1000-diff.csv"
    %"par-16000-diff.csv"
